%%%%%%%%%%%%  Generated using docx2latex.pythonanywhere.com  %%%%%%%%%%%%%%


\documentclass[a4paper,12pt]{report}

% Other options in place of 'report' are 1)article 2)book 3)letter
% Other options in place of 'a4paper' are 1)a5paper 2)b5paper 3)letterpaper 4)legalpaper 5)executivepaper


 %%%%%%%%%%%%  Include Packages  %%%%%%%%%%%%%%

\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{wasysym}
\usepackage{enumitem}
\usepackage{adjustbox}
\usepackage{ragged2e}
\usepackage{tabularx}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{hhline}
\usepackage{multicol}
\usepackage{float}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{mdwlist}
\usepackage{fancyhdr}
\usepackage[toc,page]{appendix}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}


 %%%%%%%%%%%%  Define Colors For Hyperlinks  %%%%%%%%%%%%%%


\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=cyan,
}
\urlstyle{same}


 %%%%%%%%%%%%  Set Depths for Sections  %%%%%%%%%%%%%%

% 1) Section
% 1.1) SubSection
% 1.1.1) SubSubSection
% 1.1.1.1) Paragraph
% 1.1.1.1.1) Subparagraph


\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}


 %%%%%%%%%%%%  Set Page Margins  %%%%%%%%%%%%%%


\usepackage[a4paper,bindingoffset=0.0in,headsep=0.5cm,left=0.5in,right=0.5in,bottom=0.5in,top=0.5in,headheight=2cm]{geometry}
\everymath{\displaystyle}


 %%%%%%%%%%%%  Set Depths for Nested Lists created by \begin{enumerate}  %%%%%%%%%%%%%%


\setlistdepth{9}
\newlist{myEnumerate}{enumerate}{9}
	\setlist[myEnumerate,1]{label=\arabic*}
	\setlist[myEnumerate,2]{label=\alph*}
	\setlist[myEnumerate,3]{label=(\roman*)}
	\setlist[myEnumerate,4]{label=(\arabic*)}
	\setlist[myEnumerate,5]{label=(\Alph*)}
	\setlist[myEnumerate,6]{label=(\Roman*)}
	\setlist[myEnumerate,7]{label=\arabic*}
	\setlist[myEnumerate,8]{label=\alph*}
	\setlist[myEnumerate,9]{label=\roman*}

\renewlist{itemize}{itemize}{9}
	\setlist[itemize]{label=$\cdot$}
	\setlist[itemize,1]{label=\textbullet}
	\setlist[itemize,2]{label=$\circ$}
	\setlist[itemize,3]{label=$\ast$}
	\setlist[itemize,4]{label=$\dagger$}
	\setlist[itemize,5]{label=$\triangleright$}
	\setlist[itemize,6]{label=$\bigstar$}
	\setlist[itemize,7]{label=$\blacklozenge$}
	\setlist[itemize,8]{label=$\prime$}



 %%%%%%%%%%%%  Header here  %%%%%%%%%%%%%%


%\pagestyle{fancy}
%\fancyhf{}


 %%%%%%%%%%%%  Footer here  %%%%%%%%%%%%%%

\thispagestyle{empty}


 %%%%%%%%%%%%  Print Page Numbers  %%%%%%%%%%%%%%


%\rfoot{\thepage}


 %%%%%%%%%%%%  Document Code starts here %%%%%%%%%%%%%%
\newcommand{\marginAdj}{0.5in}

\begin{document}
\sloppy

 
\begin{center}
\begin{tabular}{p{0.5\linewidth} @{\hspace{2.0cm}} p{0.5\linewidth}}

    \fontsize{20pt}{10pt}\selectfont
    \textbf{Suman Sekhar Sahoo} &
    \fontsize{10pt}{10pt}\selectfont
    {\fontsize{12pt}{12pt}\selectfont \textit{Bachelor of Engineering, BITS Pilani}\hfill\textit{}} \\

    % Bachelor of Engineering, BITS Pilani \hfill \\

    \vspace{5pt}

    \fontsize{10pt}{10pt}\selectfont
    \href{https://www.linkedin.com/in/suman-sekhar-sahoo-82621623b/}{\color{black}{\faIcon{linkedin} \smash{https://www.linkedin.com/in/suman-sekhar-sahoo-82621623b/}}} &
    \fontsize{10pt}{10pt}\selectfont
    
    \vspace{5pt}
    \href{mailto:f20212605@hyderabad.bits-pilani.ac.in}{{\color{black}\faIcon{envelope}\, f20212605@hyderabad.bits-pilani.ac.in}} \\
    
    \fontsize{10pt}{10pt}\selectfont
    \href{https://github.com/sumansekharsahoo/}{\color{black}\faIcon{github}  {\smash{https://github.com/sumansekharsahoo/}}} &
    \fontsize{10pt}{10pt}\selectfont
    \textbf{\faIcon{phone-alt}} (+91) 8610203663 \\

\end{tabular}
\end{center}

\noindent 
\textbf{EDUCATION} \par
\vspace{2pt}
\hrule
\vspace{6pt}
\noindent 
\textbf{Birla Institute of Technology and Sciences Pilani, }Hyderabad, India{\fontsize{9pt}{9pt}\selectfont \textbf{ \hspace*{0.6in} \hspace*{\marginAdj} }{\fontsize{12pt}{12pt}\selectfont Sep 2021 - May 2025}} \par
\noindent 
{\fontsize{12pt}{12pt}\selectfont \textit{Computer Science Engineering (Major) | CG: 7.96}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{12pt}{12pt}\selectfont Courses: Computer Programming, Object Oriented Programming, DBMS, Operating Systems, Theory of Computation, Machine Learning, Foundations of Data Science, Blockchain Technology} \par
\end{itemize}


 \par
 \vspace{9pt}
 
\noindent 
\textbf{EXPERIENCE} \par
\vspace{2pt}
\hrule
\vspace{6pt}


\noindent 
\textbf{SmartCBS}{\fontsize{9pt}{9pt}\selectfont \hfill  {\fontsize{12pt}{12pt}\selectfont May 2023 - Aug 2023}} \par
\noindent 
{\fontsize{12pt}{12pt}\selectfont \textit{Frontend Development Intern}\hfill\textit{Hyderabad, India}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
    \item {\fontsize{12pt}{12pt}\selectfont Established connection with an API to fetch customer data in JSON format and used React's component-based architecture to display it. } \par
    \noindent
    \item {\fontsize{12pt}{12pt}\selectfont Used context API to manage API data in a single context provider avoiding prop drilling. Styled components using Tailwind CSS} \par
    \noindent 
    \item {\fontsize{12pt}{12pt}\selectfont Technologies used: ReactJS, Context API, Tailwind CSS } \par
    \noindent
\end{itemize}



 \par
\vspace{9pt}



\noindent 
\textbf{PROJECTS} \par
\vspace{2pt}
\hrule
\vspace{6pt}

\noindent
\textbf{\href{https://github.com/sumansekharsahoo/Multithreaded-GraphDB}{\color{black}Multithreaded Distributed Graph Database}} \hfill  {\fontsize{12pt}{12pt}\selectfont Oct 2023 - Nov 2023} \par
\par
\noindent 
{\fontsize{12pt}{12pt}\selectfont \textit{Multithreading, Graph traversals, Operating System}\hfill\textit{BITS Hyd}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
    \item {\fontsize{12pt}{12pt}\selectfont Simulated a Graph Database that involved Load balancer process, Primary server and 2 Secondary servers, a Cleanup process and several Client processes.} \par
    \item {\fontsize{12pt}{12pt}\selectfont Secondary server spawns threads to serve requests of clients. Used mutex locks to prevent simultaneous write and read or write and write.} \par
    \item {\fontsize{12pt}{12pt}\selectfont Implemented multithreaded graph traversal- BFS and DFS  with semaphores.} \par
\end{itemize}

\noindent 
\textbf{\href{https://github.com/sumansekharsahoo/bits-mhsg-next}{\color{black}Full stack website for BITS MHSG}} \hfill  {\fontsize{12pt}{12pt}\selectfont July 2023 - Aug 2023} \par
\noindent
{\fontsize{12pt}{12pt}\selectfont \textit{NextJS, GraphQL, Tailwind CSS,  Hygraph, Auth}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
    \item {\fontsize{12pt}{12pt}\selectfont Developed a responsive website for BITS Mental Health Support Group using NextJS, Tailwind CSS, GraphQL and Hygraph.}  \par
    \item {\fontsize{12pt}{12pt}\selectfont Implemented Authentication using Firebase Google Auth provider. User can share playlists and post concerns regarding mental health to experts (Experts have admin page to address these issues)}  \par
    \item {\fontsize{12pt}{12pt}\selectfont Users can choose to delete their data- comments, mental health queries, Auth details.}  \par
\end{itemize}

\noindent 
\textbf{\href{https://github.com/sumansekharsahoo/DBMS-Project}{\color{black}Property rental agency database}} \hfill  {\fontsize{12pt}{12pt}\selectfont Feb 2023 - Apr 2023} \par
\noindent
{\fontsize{12pt}{12pt}\selectfont \textit{Oracle, PL-SQL}\hfill\textit{BITS Hyd}} \par
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
    \item {\fontsize{12pt}{12pt}\selectfont LDesigned a EER model and relational schema pertaining to the requirements of the rental agency. } \par
    \item {\fontsize{12pt}{12pt}\selectfont Created tables with required keys and dependencies. } \par
    \item {\fontsize{12pt}{12pt}\selectfont Created procedures and triggers to provide functionality to the database.} \par
\end{itemize}

 \par
\vspace{9pt}


\noindent 
\textbf{Skills} \par
\vspace{2pt}
\hrule
\vspace{6pt}
\noindent 
\begin{itemize}[noitemsep,topsep=0pt]
\item {\fontsize{12pt}{12pt}\selectfont Programming Language:}  C, C++, JavaScript, Java, SQL \par
\noindent 
\item {\fontsize{12pt}{12pt}\selectfont Foundational Concepts:} OOPS, DBMS, OS, Software Engineering \par
\noindent 
\item {\fontsize{12pt}{12pt}\selectfont Skills:}Frontend Development, Relational Database Management, Machine Learning \par
\noindent 
\item {\fontsize{12pt}{12pt}\selectfont Toolkits/Libraries:} ReactJS, NextJS, Redux, Linux, Git, Docker, VSCode \par
\end{itemize}

\noindent
\textbf{Position of Responsibility} \par
\vspace{2pt}
\hrule
\vspace{6pt}
\noindent 
\textbf{{\color{black}Website development team head - BITS Mental Health Support Group}} \hfill  {\fontsize{12pt}{12pt}\selectfont Jun 2023 - Present} \par
\noindent
The website development team at BITS Mental Health Support Group aims at increasing the accessibility, reach, and impact of mental health resources. As the Website Team Head, I lead a team of young developers responsible for developing and maintaining our organization's website, ensuring its functionality, usability, and visual appeal. 
\end{document}