\documentclass[10pt]{extarticle}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\begin{flushleft}
\noindent {\huge\textbf{Suman Sekhar Sahoo}}
\end{flushleft}
4th Year Undergraduate  \hfill\textbf{Phone : }+91-8610203663
\\\textbf{B.E.(Hons.),} Computer Science \hfill\textbf{Website : }\href{https://sumansekhar.vercel.app/}{sumansekhar.vercel.app}
\\\textbf{Email :} \href{mailto:sumansekharsahoo85@gmail.com}{sumansekharsahoo85@gmail.com} \hfill\textbf{GitHub :} \href{https://github.com/sumansekharsahoo}{github.com/sumansekharsahoo}
\vspace{-6pt}
\noindent\rule[0.5ex]{\linewidth}{1pt}
{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{3.5cm}|p{11cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CGPA/$\%$}\\
\hline
\centering{2021} - Present & \centering{B.Tech} & \centering{Birla Institute of Technology and Sciences Pilani, Hyderabad Campus} & 8.02/10\\
\hline
\centering{2021} & \centering{CBSE(\Romannum{12})} & \centering{Maharishi Vidya Mandir Sr. Sec. School, Chennai} & 96.8$\%$\\
\hline
\centering{2019} & \centering{CBSE(\Romannum{10})} & \centering{Maharishi Vidya Mandir Sr. Sec. School, Chennai} & 96.2$\%$\\
\hline
\end{tabular}
\end{center}
{\large \textbf{\begin{tcolorbox}\textsc{Scholastic Achievements}\end{tcolorbox}}}
\begin{itemize}
\item Secured \textbf{All India Rank 1168} in \textbf{JEE Advanced 2015} among the 1.2 Lakh shortlisted candidates.
\item Received the \textbf{Academic Excellence Award} for exceptional academic performance in 2015-16 academic session.
\item Among the top 0.3\% of the 1.5 million applicants in JEE Mains 2015.
\item Secured \textbf{Rank 1} in "Super 50" Entrance Exam conducted by Khalsa College Public School and \textbf{Government of Punjab}.
\item Received a research grant for a three months long project under the \textbf{Summer Under-graduate Research and Graduate Excellence (SURGE'17)} programme at IIT Kanpur.
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Key Projects}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Short term Traffic Prediction Using DTC} \hfill\hfill(\textit{Mar'17- Ongoing})\\\textbf{Mentor: }\textbf{Prof. Ketan Rajawat}, Department of Electrical Engineering.
\begin{itemize}
\item Implemented matrix completion via rank minimization using the \textbf{SVT (Singular Value Threshold)} algorithm.
\item Successfully implemented the \textbf{Dynamic Tensor Completion(DTC)} algorithm. It was designed in such a way so as to utilize the multimode information to forecast traffic data while maintaining the low rank constraint.
\item Collected Traffic data from PeMS and structured it into a 4-D tensor.Ran DTC on this tensor to obtain the MAE(Mean Absolute Error) close to 10. Our Future intent is to design a fast online algorithm for predicting Real time Traffic data.
\end{itemize}
\item \textbf{TV Denoising of Signals with Poisson Distribution}\hfill\hfill(\textit{May'17-Ongoing})\\\textbf{Mentor: }\textbf{Prof. Ivan Selesnick}, Department of Electrical Engineering, New York University.
\begin{itemize}
\item Learned and worked on problems related to \textbf{Sparse regularization} and \textbf{Total variation(TV)}.
\item Analyzed the differences b/w the Poisson noise and
the Gaussian noise. Determined the problems with the Poisson noise like the dependence of variance on the input signal, presence of log(x) in the fidelity term etc.
\item Implemented the total variation Denoising (TVD) algorithm for Poisson noise using alternating direction method of multipliers (ADMM). Our target is to propose a non-convex penalty(more sparse than $l_1$ norm) for the objective function.
\end{itemize}
\item \textbf{Development Intern, RTE internship, IIT Kanpur} \hfill\hfill(\textit{May'17- July'17})\\%\textbf{Mentor: }\textbf{Prof. Manindra Agrawal}, Department of Computer and Science Engineering.
\vspace{-4mm}
\begin{itemize}[label={*}]
\item \textbf{Improve Phabricator-Jenkins integration} : Show summary of compiler errors in the Jenkins comment on Phabricator. 
 \item \textbf{Fix automatic version bump setup} : Bump the version number automatically . Depending on the command ,it will bump the Major/ Minor/Patch accordingly before publishing the app.
\end{itemize}
\end{itemize}
\vspace{-2mm}
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}

%\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Programming Languages: }C, C++, HTML, \LaTeX, MATLAB, Python, Java
\item \textbf{Software and Libraries: } GNU Octave, Git, Micro-Cap , Tensor Toolbox, Jenkins, Phabricator 
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}\textsc{Positions of Responsibility}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Student Guide, Counselling Service Team}\hfill\hfill(\textit{2016-17})
\begin{itemize}
\item Guided and mentored \textbf{6 freshmen} students in acclimatizing to the Environment of the Institute. 
\item Helped them with their academics by  arranging meetings with their mentors and still maintain a good rapport with them. 
\item Coordinated with the Counselling Service and helped in the organisation of \textbf{Orientation Programme 2016}. 
%\item Helped in the \textbf{registration} of more than \textbf{800 students}, aided by other student guides
\end{itemize}
\item \textbf{Volunteer, Student Placement Office}\hfill\hfill(\textit{Nov'16-Dec'16})
\begin{itemize}
\item Managed logistics of shortlisting tests, interviews for the recruiting process.
\item Handled recruitment process of companies like Tower Research, IBM ,Edelweiss etc.
%\item Acted as a link between Placement core team, companies and Students during placement process.
\end{itemize}
\vspace{1mm}
\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Relevant Courses}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{9.8cm}|p{9.8cm}|}
\hline
Data Structure and Algorithms & Signal, Systems and Networks\\
Fundamentals of Computing &  Linear algebra and Differential Equations\\
Introduction to Electronics & Microelectronics\\
Probability and Statistics & Introduction to Economics  \\
Machine Learning, Coursera,Stanford university  & Control systems analysis\\
Digital Electronics and Microprocessor Technology*(ongoing) & Principles of Communication*(ongoing)\\
\hline
\end{tabular}
\end{center}
%\medskip
%\newpage
%\end{itemize}
{\large \textbf{\begin{tcolorbox}\textsc{Extra-Curricular Activities}\end{tcolorbox}}}
\begin{itemize}
\item Won in Volleyball event during Intramurals'15 at IIT Kanpur.
\item Part of the Runner up volleyball Team in Inferno'15, an inter-hall sports event.
%\item volunteered in various events like Techkriti (workshops), Udghosh etc.
\item Participated in Electromania in \textbf{Takneek'15}, the intra-IITK Science and Technology Championship.
\end{itemize}
\end{document}
